% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion
\usepackage{float}
\usepackage{graphicx} 
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subfigure}
\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Baoxiang Pan}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Institute of Hydrology and Water Resources, Tsinghua University}
 \moveleft.5\hoffset\centerline{Beijing 100000}
 \moveleft.5\hoffset\centerline{(86) 133-6672-0253}
  \moveleft.5\hoffset\centerline{panbaoxiang@hotmail.com}



\begin{resume}
\section{EDUCATION} {\sl Bachelor of Engineering,} Hydrology and Water Resources \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                School of Water Resources and Hydropower Engineering, Wuhan University\\ 
                \\
                {\sl Master of Engineering,} Hydrology and Water Resources \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                Institute of Hydrology and Water Resources, Tsinghua University\\ 
                expected July 2015 \\
                Concentration: Stochastic Hydrology, Hydrological Simulation 
 
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} Lisp, C, Python, \LaTeX\ ; Matlab, Mathematica, R,  Mysql,  ,Git, vim, ArcGIS, Grapher, AutoCAD .\\
                {\sl Operating Systems:} Linux, Windows.\\
                {Github URL:} https://github.com/morepenn
               
                
\section{MATH \\ SKILLS}  Analysis,
 Probability Theory, Statistics,
 Stochastic Process, Linear Algebra, Operations Research, Numerical Analysis, Information Theory, Machine Learning.
 
\iffalse
\section{ENGLISH \\ SCORES} 
\begin{minipage}{0.42\linewidth}
\begin{table}[H]\footnotesize
\begin{center}
\caption*{GRE}
\begin{tabular}{cccc}
\toprule
Verbal   & Quantity & Writing   &Total   \\
\midrule
152 & 170 & 3.5 & 322 \\  
\bottomrule
\end{tabular}
\end{center}
\end{table}
 
\end{minipage}
\hfill
\begin{minipage}{.64\linewidth}
\begin{table}[H]\footnotesize
\begin{center}
\caption*{TOEFL}
\begin{tabular}{ccccc}
\toprule
Reading & Listening  &  Speaking & Writing & Total \\ 
\midrule
29 & 27 & 20 & 26 & 102 \\  
\bottomrule
\end{tabular}
\end{center}
\end{table} 
 
\end{minipage}
  
\fi
                

\section{ACADEMIC\\WORK} {\sl Hydrological Models}   \\
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Conceptual Precipitation-Runoff Models: TOPMODEL, XINANJIANG Model, Shanbei Model, HyMod.
                \item  Water-Heat Correlation Models: Monthly Water Balance Models, Budyko.
                \item Stochastic Soil Moisture Model.
                \item  Parameter Estimation: Genetic Algorithm, Particle Swarm Optimizer, SCE-UA Algorithm. 
                \item Data-Driven Models: Support Vector Machine, Artificial Neutral Network.
                \end{itemize}
 
                {\sl Stochastic Hydrology}  \\
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Hydrological Time Series Analysis
                 \item Information Theory Applied In Hydrology
                 
                 \end{itemize} 
                 {\sl Hydrometeorology}  \\
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Boundary Layer Theory
                 \item Comparison of Evapotranspiration Equations 
                 
                 \end{itemize} 
                 {\sl Field Experiments}  \\
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Soil Characteristic Field Experiments and Hydrometeorology Observation Station Construction in the Upper Hehei Basin  
                 \item Plants and Soil-Water Characteristic Investigation in Talimu Watershed, Xinjiang Province 
                 
                 \end{itemize} 
                 \section{ACADEMIC\\EXPERIENCE}  
 {\it Presentation\\} 
 \begin{itemize}
 \item Oral Presentation in the The 2nd CAS/THU Hydrology and Water Resource Symposium
 \item Poster Presentation in the American Geophysical Union 2014 Meeting
 \item Oral Presentation in the The 3rd THU/CAS Hydrology and Water Resource Symposium
 \end{itemize}
  {\it Publication\\} 
  \begin{itemize}
  \item Pan, B. and Cong, Z.  Information Analysis of Watershed Hydrological Patterns across Temporal Scales (to be submitted). 
  \end{itemize}
 

\section{EXTRA \\ ACTIVITIES\\HOBBIES}             

            {\it Basketball}, Start S.F. of the school team. \\
            {\it Erhu}, Band 6.\\
            {\it Sketching}, Minor in Architecture in Huazhong University of Science and Technology. \\
            {\it Plat Script Writing}, Several scripts on show in the school drama club. \\
            {\it Reading}, Big fun of science philosophy and science fiction. 
 

\end{resume}
\end{document}



